# E-Commerce Sales & Customer Analytics

## 📊 Project Overview
This project simulates a real-world e-commerce database system and performs business analytics using SQL. The goal is to design a relational database and extract meaningful insights about revenue, customers, and product performance.

This project demonstrates skills relevant to data analytics, data science, information systems, and software engineering roles.

---

## 🗂 Database Design

The database consists of four main tables:

- **customers** – stores customer information  
- **products** – stores product details and inventory  
- **orders** – records customer purchases  
- **order_items** – tracks products within each order  

The schema includes:
- Primary and foreign key relationships
- NOT NULL and CHECK constraints
- Cascading deletes
- Indexes for performance optimization

---

## 🛠 Technologies Used

- MySQL  
- MySQL Workbench  
- SQL (DDL & DML)  
- Git & GitHub  

---

## 📈 Key Business Insights Generated

### 🔹 Total Revenue
Calculated total revenue from all transactions.

### 🔹 Average Order Value
Measured the average value of customer purchases.

### 🔹 Customer Lifetime Value (CLV)
Identified top customers based on total spending.

### 🔹 Top-Selling Products
Analyzed product demand by quantity sold.

### 🔹 Revenue by Category
Compared revenue across product categories.

### 🔹 Monthly Revenue Trends
Tracked sales trends over time.

---

## 🧠 Skills Demonstrated

- Relational database design  
- Data integrity enforcement  
- JOIN operations  
- Aggregation functions (SUM, AVG, GROUP BY)  
- Nested queries  
- Business analytics in SQL  
- Index optimization  
- Performance awareness  

---

## 📂 Project Structure
